The Astropy Project

### 2017-11-10 main.tex
Address Tom Rs comments about APE section

l\section*{\textit{Notes and guidelines (to be removed)}}

@@

@@

At the same time, an ecosystem of tools, programs, and webservices
has become available that makes it easier to collaborate on code development,
continuously test the code, build and provide documentation, and
supply downloadable packages. The \astropy project aims to develop and
provide high quality code and documentation according to the best
practices in software development. The project makes use of these
tools to do so without central institutional oversight.

@@

\subsection{APEs - Astropy Proposals for Enhancement}
%draft by hamogu
\inlinecomment{TODO}{subpackage vs sub-package need to be standardized throughout the paper}

\inlinecomment{Tom R}{at the moment this section doesn't take into account that APEs can be unrelated to code (e.g. APE 8 for the code of conduct)}

Central to the success of \astropy is an open environment where
anybody can contribute to the code by opening a so-called ``pull
request'' with a new code contribution on a publically available
website\footnote{\url{https://github.com/astropy/astropy}}; this
request is then reviewed by at least one of the maintainers responsible for the specific
sub-package and possibly merged into the main code base. Most bug
fixes and small features are contributed in this way. However, this
model leads to ``organic'' growth where different features are
implemented by different people with different programming styles and
interfaces. Thus, \astropy has a mechanism to more formally propose
changes to the code management (e.g.~the release cycle) or to plan
out major new features. This mechanism is called ``Astropy Proposal
for Enhancement'' (APE). In an APE one or more authors lay out a
vision for a new feature, including a rationale why this feature is
needed, how it should be implemented, and what the interface will
be \citep{ape1}. These APEs are discussed and refined before much work is invested
into a detailed implementation. APEs are again edited and discussed on
a platform\footnote{\url{https://github.com/astropy/astropy-APEs}}
open to the public. In previous APEs a community consensus emerged and
APEs are accepted and become the basis for future work at this
point. In cases where consensus cannot be reached, the
\astropy coordination committee can decide to close the discussion and
make an executive decision based on the community input on the APE in
question. APEs are modeled after the ``Python Enhancement Proposals''
(PEP) and guide the development of the \python programming language.

>>>>

\section*{\textit{Notes and guidelines (to be removed)}}

@@

\section*{Global TODO items}
\begin{itemize}
    \item subpackage vs sub-package need to be standardized throughout the paper
    \item spell check!
\end{itemize}

@@

At the same time, an ecosystem of tools, programs, and web services
has become available that makes it easier to collaborate on code development,
continuously test the code, build and provide documentation, and
supply downloadable packages. The \astropy project aims to develop and
provide high quality code and documentation according to the best
practices in software development. The project makes use of these
tools to do so without central institutional oversight.

@@

\subsection{APEs - Astropy Proposals for Enhancement}
%draft by hamogu
%edited by Adrian PW

Central to the success of \astropy is an open environment where anybody can
contribute to the project by opening a so-called ``pull request'' with a new
contribution on a publically available
website\footnote{\url{https://github.com/astropy/astropy}}.
This request is then reviewed by at least one of the maintainers responsible for
the specific subpackage or content and is possibly merged into the main code
base.
Most bug fixes, documentation edits, and small features are contributed in this
way.
However, this model leads to ``organic'' growth where different features are
implemented by different people with different programming styles and
interfaces.
Thus, \astropy has a mechanism to more formally propose significant changes to
the core package (e.g., the release cycle; \citealt{ape2}), to plan out major
new features, or institute new organization-wide policies (e.g.,
\citealt{ape8}}).
This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and are
modeled after the ``Python Enhancement Proposals'' (PEP) and guide the
development of the \python programming language.
In an APE one or more authors describe in detail the proposed changes or
additions, including a rationale for the changes, how these changes will be
implemented, and, in the case of code, what the interface will be \citep{ape1}.
The APEs are discussed and refined by the community before much work is invested
into a detailed implementation; anyone is welcome to contribute to these
discussions during the open consideration period by leaving comments on the
respective pull request.\footnote{\url{https://github.com/astropy/astropy-APEs}}
In previous APEs a community consensus emerged and APEs are accepted and become
the basis for future work at this point.
In cases where consensus cannot be reached, the
\astropy coordination committee can decide to close the discussion and
make an executive decision based on the community input on the APE in question.
